\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2017-03-18 doc/USER_MANUAL/01_introduction.tex
added a sentence about how to configure the code on CRAY machines, and added an announcement for the fact that SPECFEM3D can now perform gravity modeling in addition to seismic modeling

>>>>

\red{\Large ANNOUNCEMENT: SPECFEM3D can now perform gravity field calculations in addition (or instead of) seismic wave propagation only.
See flag \texttt{GRAVITY\_INTEGRALS} in file \texttt{setup/constants.h.in}. Please also refer to \url{http://komatitsch.free.fr/preprints/GJI_Martin_gravimetry_2017.pdf}.
And yes, that is the reason why I added a falling apple on the cover of the manual :-)}\\

### 2017-03-18 doc/USER_MANUAL/02_getting_started.tex
added a sentence about how to configure the code on CRAY machines, and added an announcement for the fact that SPECFEM3D can now perform gravity modeling in addition to seismic modeling

>>>>

If you have problems configuring the code on a Cray machine, i.e. for instance if you get an error message from the \texttt{configure} script, try exporting these two variables:
\texttt{MPI\_INC=\${CRAY\_MPICH2\_DIR}/include and FCLIBS=" "}, and for more details if needed you can refer to the \texttt{utils/Cray\_compiler\_information} directory.
